Ear canal dynamic motion piezoelectric energy harvester using a bistable oscillator cycled by coupled hydraulic switches made of collapsed flexible tubes.

### 2022-10-05 article_system.tex
update

% for cutting words
\usepackage[utf8]{inputenc}
% a font close to that chosen by Elsevier
\usepackage[bitstream-charter]{mathdesign}
\usepackage{mathtools, cuted}
% for accentuated characters
%\usepackage[T1]{fontenc}
\geometry{top=2cm,left=1.5cm,bottom=2cm,right=1.5cm}
\usepackage{multicol}
% For treating ps:
\usepackage{psfrag}
% For subfigures
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{placeins}
% For tables
\usepackage{array}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{colortbl}
\usepackage{tabulary}
\usepackage{etoolbox}
% For citations
\usepackage[numbers]{natbib}
%\biboptions{longnamesfirst,angle,semicolon}
%\citetstyle{nature}
% For color
\usepackage{color}
\usepackage{xcolor}
% For spacing
\usepackage{setspace}
%\doublespacing
\singlespacing
%\onehalfspacing
% For maths
\usepackage{amsmath, amsfonts}
\usepackage[squaren,ashgrey]{SIunits}
% For Line numbering
\usepackage[pagewise,modulo]{lineno}
%\linenumbers
% For special characters
\usepackage{pifont}
%
\usepackage[pagebackref,colorlinks=True]{hyperref}
\usepackage{wasysym}
\usepackage{color}
\usepackage{cleveref}
\crefformat{figure}{(Fig.~#2#1#3)}
\usepackage{hyperref}
\usepackage[hyperpageref]{backref}
\usepackage{lipsum}
\usepackage{booktabs} % To thicken table lines
% \usepackage{widetext}
\usepackage{float}
\usepackage{empheq}

%----------------------------------------------------------------------
%                     Commands
%----------------------------------------------------------------------
\renewcommand*{\overrightarrow}[1]{\vbox{\halign{##\cr \tiny\rightarrowfill\cr\noalign{\nointerlineskip\vskip1pt}$#1\mskip2mu$\cr}}}
%% Degree character
\DeclareTextSymbol{\degr}{T1}{6}
\newcommand{\degre}[0]{\degr C}
\DeclareUnicodeCharacter{2212}{-}
% MPam^0.5 character
\newcommand{\mpa}[0]{\mbox{MPa}\sqrt{\mbox{m}}}
%mettre de nouilles sous les tenseurs
\newcommand{\ve}[1]{{\underline{#1}}}
\def\ten#1{\oalign{$#1$\crcr\hidewidth$\scriptscriptstyle\sim$\hidewidth}} 
% derivee seconde
\newcommand{\fda}[2]{\displaystyle \frac{\partial\,{#1}}{\partial\, {#2}}}
% et al. for citations
\newcommand{\etal}[0]{{\em et al.}}
\renewcommand*\contentsname{\large{Table of contents}}
\def \hfillx {\hspace*{ -\linewidth} \hfill} % remplir espacement horizontal entre deux sous-figures de façon à remplir toute la largeur du texte.
%----------------------------------------------------------------------
%                     Colors
%----------------------------------------------------------------------
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
%----------------------------------------------------------------------
%                     Pre-Document
%----------------------------------------------------------------------
\journal{Applied Energy}
%----------------------------------------------------------------------
%                     Document
%----------------------------------------------------------------------
\begin{document}

@@

Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system. The theoretical global efficiency of the harvester is evaluated at $\eta_g=67.1$\% with 20µJ harvested from one mastication. The energy losses are mostly located in the BO stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BO architectures \cite{Liu2013}. The energy source depends on the comfort pressure level $p_c$ that is set to 1kPa here, i.e. a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}. The harvester efficiency could lead to a theoretical maximum of $342$µJ extractable from the ear canal.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.5cm},clip, width=\textwidth]{figures/positions+DeltaV_debits_pear.pdf}
	\caption{}
	\label{fig:positions+DeltaV_debits_pear}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.9cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
	\caption{}
	\label{fig:positions_Up_puissances_energies}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{table}	
	\centering
	\begin{tabular}{c|c|c}
\toprule
\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
\midrule
$K$					&	0.256			& [$N/\mu m$]			\\ \hline
$x_0$				&	0.49			& [$mm$] 				\\ \hline
$L$					&	16.0			& [$mm$] 				\\ \hline
$m$					&	5.88			& [$g$] 				\\ \hline
$x_{c0}$			&	0.69			& [$mm$] 				\\ \hline
$R_{ch}$			&	15.5			& [$k\Omega$] 			\\ \hline
$\alpha$			&   0.105			& [$N/V$] 				\\ \hline
$C_0$	   			&	0.25			& [$\mu F$]				\\ \hline
$Q$ 				&	50				& [-] 					\\ \hline
$\eta_g$			& 	76				& [$\%$]		\\ 
\bottomrule
	\end{tabular}
	\caption{Electromechanical parameters}
	\label{tab:parametres électromécaniques}
\end{table}
\begin{table}
	\centering
	\begin{tabular}{c|c|c}
\toprule
\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
\midrule
$D_{hc}$  	   				&	4				& [$mm$]			\\ \hline
$a_h$					&	7.2				& [-]				\\ \hline
$p_c$					&	1				& [$kPa$]			\\ \hline
$\Delta V{ear,m}$		& 60				& [$mm^3$]			\\ \hline
$Cf_0$					&	0.21e17			&[$Pa.s^2m^{-6}$]	\\ \hline
$Cf_c$					&	5.46e17			&[$Pa.s^2m^{-6}$]	\\
\bottomrule 
	\end{tabular}
	\caption{Hydraulic parameters}
	\label{tab:parametres_hydrauliques}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The device heart is the electromechanical converter composed of the BO implementing the APG and therefore, they have been designed with respect to space requirements. We opted for a monobloc structure with blades in order to optimize the oscillator quality factor by avoiding screw assemblies. Figure \ref{fig:monobloc_face} shows the face view of the monobloc bistable oscillator CAD that has been fabricated by electrical discharge machining (EDM). The 8 hinges are assured by 4 buckled blades (BB) and a vertical guide blade (GB) ensures the APG mounting. The efficient part composed of the blades and the central mass are $1.2$mm think. The external rigid $6$mm thick frame has been designed to ensure the fixed boundary conditions and also to allow the mounting of both the measurement instruments and the HCs. The local thickenings at the midspan of the blades are intended to facilitate the fabrication and also to maximize the BB compression stiffness that maximizes the electromechanical coupling of the harvester, as we show in the following sections. The geometrical and mechanical parameters of the BO are referenced in table \ref{tab:parametres_lames}. The following sections describe the design method that led to the dimensions of the blades that depend on our needs.

@@

$K_{bb}$ is for its part verified through a FEM generated with the BO CAD on ANSYS Workbench. Figure \ref{fig:fem_statique} presents the model and the initial and boundary conditions used for the study. The fixed frame is replaced by three rigid fixed points in order to minimize the number of elements and reduce the calculation time. The APG elastic force is modeled by the load $F_{st}$ applied at the right end of the structure and the transducer is replaced by a rigid mobile part in order to isolate the stiffness of the BBs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
\centering
\captionsetup{justification=centering}
	\includegraphics[trim={21.9cm 0cm 0cm 10.2cm},clip,width=.8\linewidth]{figures/fem_statique.pdf}
	\caption{BO finit element model}
\label{fig:fem_statique}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
By imposing incrementally increasing $F_{st}$ and measuring the displacement $z_{st}$ of the moving structure in small displacement condition, we can determine $K_{bb}$ (tab. \ref{tab:parametres_lames}) with equation \ref{eq:Kbb_definition}.
\begin{equation}
	K_{bb} = \dfrac{F_{st}}{z_{st}}
	\label{eq:Kbb_definition}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The stiffness of the BBs and the GB lead to a theoretical efficiency of 75\%, which is consistent with the previous simulated results (\ref{tab:parametres électromécaniques}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={1cm 3cm 2cm 2.5cm},clip,width=0.45\textwidth]{figures/BDT_OB+GPA.pdf}
	\caption{Vue de face de GPA et l’OB monobloc sur le banc de caractérisation
	électromécanique.}
	\label{fig:BDT_OB+GPA}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
\captionsetup{justification=centering}
	\begin{tabular}{ c | c | c }
	\toprule
	& \textbf{Simulation with}  	   & \textbf{Simulation with}        \\
	& \textbf{theoretical}  		   & \textbf{recalibrated }			 \\
	\multirow{-3}{*}{\textbf{Symbol}}
	& \textbf{parameters}			   & \textbf{parameters} 			 \\
	\midrule
	$Q$                       & 50.0                  & 30.0 		  	\\  
	$f_0$                     & 47.0 Hz               & 27.9 Hz  		\\
	$x_0$                     & 0.49 mm               & 0.50 mm    		\\
	$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
	${k^2_{sys}}$             & 8.72 \%               & 1.25 \% 		\\
	$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\
	\bottomrule
	\end{tabular}
	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
	\label{tab:parametres_lacher_free}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%

>>>>

% for cutting words
\usepackage[utf8]{inputenc}
% a font close to that chosen by Elsevier
\usepackage[bitstream-charter]{mathdesign}
\usepackage{mathtools, cuted}
% for accentuated characters
%\usepackage[T1]{fontenc}
\geometry{top=2cm,left=1.5cm,bottom=2cm,right=1.5cm}
\usepackage{multicol}
% For treating ps:
\usepackage{psfrag}
% For subfigures
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{placeins}
% For tables
\usepackage{array}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{colortbl}
\usepackage{tabulary}
\usepackage{etoolbox}
% For citations
\usepackage[numbers]{natbib}
%\biboptions{longnamesfirst,angle,semicolon}
%\citetstyle{nature}
% For color
\usepackage{color}
\usepackage{xcolor}
% For spacing
\usepackage{setspace}
%\doublespacing
\singlespacing
%\onehalfspacing
% For maths
\usepackage{amsmath, amsfonts}
\usepackage[squaren,ashgrey]{SIunits}
% For Line numbering
\usepackage[pagewise,modulo]{lineno}
%\linenumbers
% For special characters
\usepackage{pifont}
%
\usepackage[pagebackref,colorlinks=True]{hyperref}
\usepackage{wasysym}
\usepackage{color}
\usepackage{cleveref}
\crefformat{figure}{(Fig.~#2#1#3)}
\usepackage{hyperref}
\usepackage[hyperpageref]{backref}
\usepackage{lipsum}
\usepackage{booktabs} % To thicken table lines
% \usepackage{widetext}
\usepackage{float}
\usepackage{empheq}
\usepackage{textcomp}

%----------------------------------------------------------------------
%                     Commands
%----------------------------------------------------------------------
\renewcommand*{\overrightarrow}[1]{\vbox{\halign{##\cr \tiny\rightarrowfill\cr\noalign{\nointerlineskip\vskip1pt}$#1\mskip2mu$\cr}}}
%% Degree character
\DeclareTextSymbol{\degr}{T1}{6}
\newcommand{\degre}[0]{\degr C}
\DeclareUnicodeCharacter{2212}{-}
% MPam^0.5 character
\newcommand{\mpa}[0]{\mbox{MPa}\sqrt{\mbox{m}}}
%mettre de nouilles sous les tenseurs
\newcommand{\ve}[1]{{\underline{#1}}}
\def\ten#1{\oalign{$#1$\crcr\hidewidth$\scriptscriptstyle\sim$\hidewidth}} 
% derivee seconde
\newcommand{\fda}[2]{\displaystyle \frac{\partial\,{#1}}{\partial\, {#2}}}
% et al. for citations
\newcommand{\etal}[0]{{\em et al.}}
\renewcommand*\contentsname{\large{Table of contents}}
\def \hfillx {\hspace*{ -\linewidth} \hfill} % remplir espacement horizontal entre deux sous-figures de façon à remplir toute la largeur du texte.
% \renewcommand{\degree}[1]{${#1}^\circ$} % °

%----------------------------------------------------------------------
%                     Colors
%----------------------------------------------------------------------
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
%----------------------------------------------------------------------
%                     Pre-Document
%----------------------------------------------------------------------
\journal{Applied Energy}
%----------------------------------------------------------------------
%                     Document
%----------------------------------------------------------------------
\begin{document}

@@

Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system. The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=76$\%} with 20µJ harvested from one mastication. The energy losses are mostly located in the BO stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BO architectures \cite{Liu2013}. The energy source depends on the comfort pressure level $p_c$ that is set to 1kPa here, i.e. a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}. The harvester efficiency could lead to a theoretical maximum of $684$µJ extractable from the ear canal.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.5cm},clip, width=\textwidth]{figures/positions+DeltaV_debits_pear.pdf}
	\caption{}
	\label{fig:positions+DeltaV_debits_pear}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 1cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
	\caption{}
	\label{fig:positions_Up_puissances_energies}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{table}	
	\centering
	\begin{tabular}{c|c|c}
\toprule
\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
\midrule
$K$					&	0.256			& [$N/\mu m$]			\\ \hline
$x_0$				&	0.49			& [$mm$] 				\\ \hline
$L$					&	16.0			& [$mm$] 				\\ \hline
$m$					&	5.88			& [$g$] 				\\ \hline
$x_{c0}$			&	0.69			& [$mm$] 				\\ \hline
$R_{ch}$			&	6.39			& [$k\Omega$] 			\\ \hline
$\alpha$			&   0.105			& [$N/V$] 				\\ \hline
$C_0$	   			&	0.25			& [$\mu F$]				\\ \hline
$Q$ 				&	50				& [-] 					\\ \hline
$\eta_g$			& 	76				& [$\%$]		\\ 
\bottomrule
	\end{tabular}
	\caption{Electromechanical parameters}
	\label{tab:parametres électromécaniques}
\end{table}
\begin{table}
	\centering
	\begin{tabular}{c|c|c}
\toprule
\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
\midrule
$D_{hc}$  	   			&	4				& [$mm$]			\\ \hline
$a_h$					&	29				& [-]				\\ \hline
$p_c$					&	1				& [$kPa$]			\\ \hline
$\Delta V{ear,m}$		& 60				& [$mm^3$]			\\ \hline
$Cf_0$					&	0.21e17			&[$Pa.s^2m^{-6}$]	\\ \hline
$Cf_c$					&	5.46e17			&[$Pa.s^2m^{-6}$]	\\
\bottomrule 
	\end{tabular}
	\caption{Hydraulic parameters}
	\label{tab:parametres_hydrauliques}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The device heart is the electromechanical converter composed of the BO implementing the APG and therefore, they have been designed with respect to space requirements. We opted for a monobloc structure with blades in order to optimize the oscillator quality factor by avoiding screw assemblies. Figure \ref{fig:monobloc_face} shows the face view of the monobloc bistable oscillator CAD that has been fabricated by electrical discharge machining (EDM). The 8 hinges are assured by 4 buckled blades (BB) while a vertical guide blade (GB) ensures the APG mounting and avoids any of its rotations. The efficient part composed of the blades and the central mass are $1.2$mm think. The external rigid $6$mm thick frame has been designed to ensure the fixed boundary conditions and also to allow the mounting of both the measurement instruments and the HCs. The local thickenings at the midspan of the blades are intended to facilitate the fabrication and also to maximize the BB compression stiffness that maximizes the electromechanical coupling of the harvester, as we show in the following sections. The geometrical and mechanical parameters of the BO are referenced in table \ref{tab:parametres_lames}. The following sections describe the design method that led to the dimensions of the blades that depend on our needs.

@@

$K_{bb}$ is for its part verified through a FEM generated with the BO CAD on ANSYS Workbench. Figure \ref{fig:fem_statique} presents the model and the initial and boundary conditions used for the study. The fixed frame is replaced by three rigid fixed points in order to minimize the number of elements and reduce the calculation time. The APG elastic force is modeled by the load $F_{st}$ applied at the right end of the structure and the transducer is replaced by a rigid mobile part in order to isolate the stiffness of the BBs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
\centering
\captionsetup{justification=centering}
	\includegraphics[trim={21.9cm 0cm 0cm 10.2cm},clip,width=.8\linewidth]{figures/fem_statique.pdf}
	\caption{BO finit element model with initial and boundary conditions for a static study}
\label{fig:fem_statique}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
By imposing incrementally increasing $F_{st}$ and measuring the displacement $z_{st}$ of the moving structure in small displacement condition, we can determine $K_{bb}$ (tab. \ref{tab:parametres_lames}) with equation \ref{eq:Kbb_definition}. The stiffness of the BBs and the GB lead to a theoretical efficiency of 75\%, which is consistent with the previous simulated results (tab. \ref{tab:parametres électromécaniques}).
\begin{equation}
	K_{bb} = \dfrac{F_{st}}{z_{st}}
	\label{eq:Kbb_definition}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to preserve an adequate mechanical transmission from the mass to the APG, we must ensure that no secondary buckling mode does appear on the BBs during the BO operation. Based on the precedent FEM static model (fig. \ref{fig:fem_statique}), a buckling study has been performed for the purpose. When the mass crosses the unstable \mbox{$x_m=0$} position, the compression stress on the blades is in fact at its maximum. With the same boundary conditions as in figure \ref{fig:fem_statique}, the buckling study imposes the force $F_{st} = F_{z,0}$ modeling the APG elastic counter reaction on $\vec{z}$ axis at $x_m = 0$. $F_{z,0}$ can be expressed by equation \ref{eq:Fz0_flambement} relying on figure \ref{fig:schema_cinematique1} :
\begin{equation}
	F_{z,0} = 2K \biggl( \sqrt{x_0^2+L^2}-L \biggr)
	\label{eq:Fz0_flambement}
\end{equation}

The fundamental buckling mode of the BBs leads to the wanted structural buckling generating the bistable equilibrium positions $\pm x_0$ for the mass. The buckling study reveals that $F_{z,0}=0.61$N when the useful buckling mode appears (fig. \ref{fig:buckling_fundamental}). However, the first secondary undesirable mode illustrated on figure \ref{fig:buckling_secondary} appears for $F_{z,0}=6.4$N.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{figure}[!htb]
	\begin{center}
		\begin{subfigure}[t]{0.48\linewidth}
			\captionsetup{justification=centering}
			\includegraphics[trim={24.1cm 0cm 0cm 14.8cm},clip,width=\linewidth]{figures/buckling_fundamental.pdf}
			\caption{Fundamental = useful}
			\label{fig:buckling_fundamental}
		\end{subfigure}
		\hfillx
		\begin{subfigure}[t]{0.48\linewidth}
			\captionsetup{justification=centering}
			\includegraphics[trim={24.1cm 0cm 0cm 14.8cm},clip,width=\linewidth]{figures/buckling_secondary.pdf}
			\caption{Secondary = undesirable}
			\label{fig:buckling_secondary}
		\end{subfigure}
		\caption{Deformed shape of the first appearing buckling modes}
		\label{fig:Buckling_deformed_shapes}
	\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
The secondary buckling modes absorb mechanical energy that is not transmitted to the APG and therefore can not be converted in electricity. Therefore, it is preferable to avoid them by establishing a buckling height domain for the fabricated BO, as presented on figure \ref{fig:buckling_limit}. The preliminary simulated case presented in the previous section is well located in the preferable domain where there is no undesirable buckling modes. Moreover, the force absorbed by the APG is well under the maximal limit of 18N from which the device could be damaged.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={17.9cm 0cm 0cm 10cm},clip,width=0.9\linewidth]{figures/buckling_limit.pdf}
	\caption{APG elastic counter reaction on $\vec{z}$ axis at $x_m=0$, depending on the initial structural buckling height $x_0$}
	\label{fig:buckling_limit}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ltex language=en

    %///////////////////////////////////////////// 
	\subsection{Experimental characterizations}	
	\label{subsec:Experimental characterizations}
    %/////////////////////////////////////////////
The BO has been fabricated and mounted and the APG has been implemented on it. The experimental test bench for the electromechanical characterizations of the resultant converter is presented on figure \ref{fig:BDT_OB+GPA}. An additional blade is mounted with the APG in order to prevent its rotation around any axis. A micrometric screw helps to set the initial structural buckling level $x_0$ ($\pm 10$µm). The bearing decouples the rotation of the screw with the rotation of the blade structure in order to prevent unwanted torsional stress. Two symmetrically mounted masses are added on the initial central mass with a 45\degree{} machined plane. The latter receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position of the mas along $\vec{x}$ axis ($\pm 10$µm). The APG power is dissipated in the $R_{ch}$ resistor and the $U_p$ tension ($\pm 1$mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface. Finally, the two HC plungers actuate the mass from one stable equilibrium position to the other.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={2cm 0cm 0cm 5.5cm},clip,width=\linewidth]{figures/BDT_OB+GPA.pdf}
	\caption{Test bench of the electromechanical converter}
	\label{fig:BDT_OB+GPA}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The HV mechanical influence is not considered in order to isolate the electromechanical converter dynamic behavior. The test protocol consisted on recreating the operation conditions as close as possible to real-life operation. The mass is guided from a stable equilibrium position until it reaches \mbox{$x_m=0$}, and then it goes oscillate around the opposite stable equilibrium position. The experimental data was then used to identify and recalibrate the following electromechanical parameters of the harvester through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (tab. \ref{tab:parametres_lacher_free}). The correlations were made with iterative simulations of the global model by minimizing the error on these parameters. The converter experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{bo}$ have also been extracted from the recalibrated model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={17cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/correlation_simu-exp_OB+GPA.pdf}
	\caption{Experimental measurements and global system simulation with the identified parameters of table \ref{tab:parametres_lacher_free}.}
	\label{fig:BDT_OB+GPA}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
	\centering
	\captionsetup{justification=centering}
		\begin{tabular}{ c | c | c }
		\toprule
		& \textbf{Simulation with}  	   & \textbf{Simulation with}        \\
		& \textbf{theoretical}  		   & \textbf{recalibrated }			 \\
		\multirow{-3}{*}{\textbf{Symbol}}
		& \textbf{parameters}			   & \textbf{parameters} 			 \\
		\midrule
		$Q$                       & 50.0                  & 30.0 		  	\\  
		$f_0$                     & 47.0 Hz               & 27.9 Hz  		\\
		$x_0$                     & 0.49 mm               & 0.50 mm    		\\
		$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
		${k^2_{sys}}$             & 16 \%                 & 1.25 \% 		\\
		$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\
		\bottomrule
		\end{tabular}
		\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
		\label{tab:parametres_lacher_free}
	\end{table} 
	%%%%%%%%%%%%%%%%%%%%%
